A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-22 tex/codatadp.tex
more

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\MIDRULE
No (co)datatypes
  & 221 & 760 & \phantom{0}57 & 1038 \\[\jot]
Datatype simplication only
  &  \\
Datatypes without acyclicity
  & \bfseries 227 & 765 & \phantom{0}57 & 1049 \\
Datatypes with acyclicity
  & \bfseries 227 & 771 & \phantom{0}57 & 1055 \\[\jot]
Codatatype simplication only
  &  \\
Codatatypes without uniqueness
  & 217 & 787 & \phantom{0}55 & 1059 \\
Codatatypes with uniqueness
  & 218 & 787 & \bfseries \phantom{0}58 & 1063 \\[\jot]
Full (co)datatypes
  & 224 & \bfseries 798 & \bfseries \phantom{0}58 & \bfseries 1080 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 317 & 4170
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

>>>>

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\MIDRULE
No (co)datatypes
  & 221 & 760 & \phantom{0}55 & 1036 \\[\jot]
%Datatype simplication only
%  &  \\
Datatypes without acyclicity
  & \bfseries 227 & 765 & \phantom{0}55 & 1047 \\
Datatypes with acyclicity
  & \bfseries 227 & 771 & \phantom{0}55 & 1053 \\[\jot]
%Codatatype simplication only
%  &  \\
Codatatypes without uniqueness
  & 215 & 789 & \phantom{0}56 & 1060 \\
Codatatypes with uniqueness
  & 216 & 789 & \bfseries \phantom{0}59 & 1064 \\[\jot]
Full (co)datatypes
  & 222 & \bfseries 800 & \bfseries \phantom{0}59 & \bfseries 1081 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 317 & 4170
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}
